---
title: "Assignment 1"
author: "Kunal Sharma"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message =  FALSE)
```
## Importing Important Packages
```{r}
library(ISLR)
library(dplyr)
library(ggplot2)
```

Loading the Carseats dataset with only 3 variables.
Filtering the data into two subsets based on the shelve location(GOOD or BAD).

```{r}
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")
Good_shevles <- filter(SafeBabies, ShelveLoc == "Good")
Bad_shevles <- filter(SafeBabies, ShelveLoc == "Bad")
```

#Building a Linear Regression model to predict the sales of the carseat for both good as well as bad shelve location individually.

```{r}
#Linear Model for GOOD Shelve location
Lm_Good <- lm(Sales ~ Price, data = Good_shevles)
summary(Lm_Good)
```

```{r}
#Linear Model for BAD Shelve location
Lm_Bad <- lm(Sales ~ Price, data = Bad_shevles)
summary(Lm_Bad)
```

#Equation:
Total Profit = Sales * (Selling Price - Production Cost)

Futher simplication of equation we got the below formula,

Optimal Selling Price = Predicted Sales based on Production Cost / (2 * Estimated Price Coefficient)

Assuming the Production Cost of a CarSeat is $55.0, below is the predicted optimal Selling Price of the Carseat.

## optimal cost for shelve location Good ##
```{r}
Productioncost<-55
paste("The optimal price for a good shelf position", ((-Lm_Good$coefficients[[2]] *Productioncost) + (Lm_Good$coefficients[[1]]))/(-2 * Lm_Good$coefficients[[2]]))
```
## optimal cost for shelve location bad ##
```{r}
paste("The optimal price for a bad shelf position", ((-Lm_Bad$coefficients[[2]] *Productioncost) + (Lm_Bad$coefficients[[1]]))/(-2 * Lm_Bad$coefficients[[2]]))
```
Note: The negative sign is inserted in the denominator to nullify the negation, as the sign of the LM shows Price's negative correlation with the intercept (Sales).

Here the variation in Production Cost from $40 to $85 the Selling Price also varies as below.

```{r}
Good_Optimal_price_Range <- (predict(Lm_Good, data.frame(Price = c(40:85)))) / (-2*Lm_Good$coefficients[2])
Bad_Optimal_Price_Range <- (predict(Lm_Bad, data.frame(Price = c(40:85)))) / (-2*Lm_Bad$coefficients[2])
```

Selling Price for Good and Bad Shelve Locations over Production Costs of $40-$85

```{r}
Price_Range<- cbind.data.frame(Production_Cost = c(40:85), Selling_Price_Good = Good_Optimal_price_Range, Selling_Price_Bad = Bad_Optimal_Price_Range)
Price_Range
```

The variations of Price for both good and bad shelve locations is represented graphically below.

```{r}
ggplot(Price_Range, aes(Production_Cost, Price_Range)) + geom_line(aes(y = Good_Optimal_price_Range, col = "Good Shelve")) + geom_line(aes(y = Bad_Optimal_Price_Range, col = "Bad Shelve"))
```

